\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{xcolor}
\usepackage{paracol}
\usepackage{helvet}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{microtype}
\input{glyphtounicode}

% Color scheme
\definecolor{accent}{RGB}{0,160,210}

% Font
\usepackage{newpxtext}
\linespread{1.05}
\usepackage[T1]{fontenc}

% Page geometry
\geometry{a4paper, top=1.4cm, bottom=1.4cm, left=1.5cm, right=1.5cm}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{%
  \ifnum\value{page}=2
    \parbox{\textwidth}{%
      \centering\tiny\textit{I agree to~the processing of~personal data provided in~this document for realising the recruitment process pursuant to~the Personal Data Protection Act of~10~May 2018 (Journal of~Laws 2018, item 1000) and in~agreement with Regulation (EU) 2016/679 of~the European Parliament and of~the Council of~27~April 2016 on~the protection of~natural persons with regard to~the processing of~personal data and on~the free movement of~such data, and repealing Directive 95/46/EC (General Data Protection Regulation).}%
    }%
  \fi
}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}
\setlength{\columnsep}{15pt}

% Disable hyphenation completely
\hyphenpenalty=10000
\exhyphenpenalty=10000
\sloppy

% Sections: bold uppercase with horizontal rule
\titleformat{\section}{
  \vspace{2pt}\bfseries\raggedright\normalsize
}{}{0em}{\MakeUppercase}[\color{black}\titlerule\vspace{-2pt}]

% ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\cvitem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\cvitemstart}{\begin{itemize}[leftmargin=*,label=\textbullet,topsep=1pt,itemsep=0pt,parsep=0pt]\small}
\newcommand{\cvitemend}{\end{itemize}\vspace{2pt}}
\newcommand{\entrysep}{%
  \vspace{3pt}%
  \noindent{\color{black!25}\dotfill}%
  \vspace{5pt}\par%
}

\begin{document}

% ---- HEADER ----
{\fontsize{34}{40}\selectfont\bfseries\sffamily Katarzyna Gryta}\par
\vspace{2pt}
{\large\bfseries\textcolor{accent}{Medical Information and AE~Intake, Master of~Pharmacy}}\par
\vspace{6pt}
\small
\faPhone\enspace\href{tel:+48501581731}{+48 501 581 731}\quad
\faEnvelope\enspace\href{mailto:kasia.gryta@gmail.com}{kasia.gryta@gmail.com}\quad
\faLinkedin\enspace\href{https://www.linkedin.com/in/kgryta/}{https://www.linkedin.com/in/kgryta/}\par
\normalsize\vspace{8pt}

% ---- TWO-COLUMN LAYOUT ----
\columnratio{0.63}
\begin{paracol}{2}

%% ---- LEFT COLUMN ---- %%

\section{Experience}

\noindent\small Jun. 2025 -- currently\par
\noindent\textcolor{accent}{\textbf{Operations Specialist I}}\quad\textbf{IQVIA} $|$ Warsaw\par
\noindent\small\textit{(Medical Information and \mbox{AE~Intake} Specialist for AstraZeneca and Sobi)}\par
\vspace{2pt}
\cvitemstart
  \cvitem{Provide phone support to~HCPs and consumers regarding AEs, PQCs, medical inquiries, product support and other needs as~required}
  \cvitem{Receive, triage, review and process Lifecycle safety operational data}
  \cvitem{Perform data entry for tracking and Lifecycle safety databases, coding relevant medical terminology, writing descriptive narratives, generating queries pertinent to~the case, performing quality control, assisting with reconciliation, driving case closure, coordinating translations}
  \cvitem{Receive and document incoming telephone calls or~emails from investigative sites or~other sources reporting safety data}
\cvitemend

\noindent\underline{\small Achievements:}
\cvitemstart
  \cvitem{Provided multiple materials to~the HCPs based on~medical literature}
  \cvitem{Responded to~various safety and \mbox{non-medical} queries regarding medicines using information from SmPCs and PILs}
  \cvitem{Collected quality complaints related to~defective products, contributing to~the prevention of~future quality issues}
  \cvitem{Communicated with the customers from US~and CA~regarding reported AEs~to~obtain information relevant to~human safety}
\cvitemend

\entrysep

\noindent\small Apr. 2024 -- May 2025\par
\noindent\textcolor{accent}{\textbf{Clinical Trial Assistant}}\quad\textbf{ICON plc} $|$ Warsaw\par
\vspace{2pt}
\cvitemstart
  \cvitem{Administration, coordination, and management of~delegated study activities}
  \cvitem{Assisting with CRA/SMA tasks, in~the \mbox{on-site} Monitoring Visit, with the document collection from sites and generating study reports}
  \cvitem{Preparing, signing and delivering submission documents for Germany}
  \cvitem{Coordinating document translation from the local language}
  \cvitem{Planning and coordinating internal and external meetings}
  \cvitem{Reviewing and managing the Trial Master File (TMF)}
\cvitemend

\noindent\underline{\small Achievements:}
\cvitemstart
  \cvitem{Closed out a~global paper study that had been ongoing for several years. Managed study documentation and coordinated communication between CRAs and CMAs}
  \cvitem{Participated in~the Monitoring Visit, during which study documentation was verified. Communicated with the PI~and pharmacist. Verified medical records, consent forms and drug supplies. Supported CRAs with assigned tasks.}
  \cvitem{Prepared and submitted documents in~German to~medical institutions and supported the SSUA team}
  \cvitem{Organized and recorded study documentation using MS~Office tools}
  \cvitem{Provided mentoring and support to~team members as~a~mentor}
  \cvitem{Achieved \mbox{highly-successful} opinion from the manager and team}
\cvitemend

\newpage

\section{Activity}

\noindent\small Sep. 2021 -- Mar. 2024\par
\noindent\textbf{UW Incubator} $|$ University of~Warsaw\par
\cvitemstart
  \cvitem{BraveCamp (sponsored by~Pfizer) $|$ Feb. 2023}
  \cvitem{Biotech Leaders Academy by~Roche $|$ Oct.--Dec. 2021}
\cvitemend

\entrysep

\noindent\small 2020 -- Mar. 2024\par
\noindent\textbf{Student Research Club ``Free Radicals''} of~Pharmacy Faculty $|$ MUW\par
\cvitemstart
  \cvitem{Present study of~the resveratrol antioxidant capacity in~wines}
  \cvitem{Participation in~meetings and web conferences}
\cvitemend

\entrysep

\noindent\small Mar. 2012 -- Jul. 2022\par
\noindent\textbf{Intern} -- Institute of~Physical Chemistry $|$ Polish Academy of~Sciences $|$ Warsaw\par
\cvitemstart
  \cvitem{Polymer electrocatalysts -- application of~conductive polymer films as~a~selective electrocatalysts}
  \cvitem{Data analytics using OriginPro}
\cvitemend

\section{Language Courses}

\noindent\small 2023 -- currently\par
\noindent\textbf{Osterreich Institut} $|$ Warsaw\par
\noindent\small German $|$ B2.2\par

%% ---- RIGHT COLUMN ---- %%
\switchcolumn

\section{Skills}

\noindent\small MS~Office -- Argus -- Veeva Vault -- Management -- Analytical: Power BI, Power Automate, AICopilotPro -- Figma -- Canva -- Leadership -- Driver's License B\par

\vspace{6pt}

\section{Education}

\noindent\small 2018 -- 2024\par
\noindent\textbf{Medical University of~Warsaw}\par
\noindent\small Faculty of~Pharmacy\par
\noindent\textcolor{accent}{\textbf{Pharmacy}}\par
\noindent\small Specialisation: Individual Studies in~Drug Design\par

\vspace{6pt}

\section{Languages}

\noindent\small Polish (Native)\par
\noindent\small English (Advanced)\par
\noindent\small German (Intermediate) 2023 -- currently\par

\vspace{6pt}

\section{Publication}

\noindent\small\href{https://doi.org/10.25121/PF.2022.23.2.85}{\textit{``Resveratrol -- structure, properties and effect on the human body''}}\par
\vspace{2pt}
\noindent\small Review paper created as~a~member of~the Student Research Club -- Free Radicals in~Medical University of~Warsaw\par
\noindent\small Magazine: \textit{``Postępy Fitoterapii''}\par

\vspace{6pt}

\section{Other Education}

\noindent\small Mar. 2024\par
\noindent\small ICH GCP E6 R2\par
\noindent\small Certificate $|$ The Global Health Network\par

\vspace{4pt}

\noindent\small Feb. 2022\par
\noindent\small Pharmacovigilance and Regulatory Affairs\par

\vspace{4pt}

\noindent\small Apr. 2021\par
\noindent\small Clinical Trials\par
\noindent\small Certificate $|$ Education for Business and Science\par

\vspace{6pt}

\section{Hobby}

\noindent\small Sailing (Younger Sailing Instructor) -- Dancing -- Music (Musical School)\par

\end{paracol}

\end{document}
